\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://github.com/Glqzer/}{\Large David Wang}} & Email : \href{mailto:davidlwang2004@gmail.com}{davidlwang2004@gmail.com}\\
  \href{http://www.github.com/Glqzer/}{http://www.github.com/Glqzer} & Mobile : \href{tel:+15853511507}{+1-585-351-1507} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Johns Hopkins University}{Baltimore, MD}
      {B.S. in Computer Science, B.S. in Applied Mathematics and Statistics}{2026}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
 \section{Applicable Skills}
{C++, C, Java, JavaScript, Python, Go, SQL, OCaml, HTML, CSS, Swift, Git, LaTeX, AWS (Redshift)}

%-----------APPLIED EXPERIENCE-----------------
\section{Applied Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Johns Hopkins University}{Baltimore, MD}
      {Marketing Data Analyst}{March 2024 - Present}
      \resumeItemListStart
        \resumeItem{Data Collection}
          {Integratated data from CRM systems, website analytics, and social media platforms to create a comprehensive view of consumer behavior and to increase campaign engagements by 40\%. }
        \resumeItem{Performance Metrics}
          {Collaborated on A/B testing to evaluate effective strategies and identify optimal elements in campaigns.}
        \resumeItem{Customer Prediction Models}
          {Built predictive models for customer churn prediction and utilized pre-trained models for text classification and translation.}
        
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Apple PSI Protocol}
      {Implementation of Apple's private set intersection protocol for detecting CSAM image material.}
    \resumeSubItem{Healthcare AI iOS Application}
      {Health application using ChatGPT AI and Google Maps API to search symptoms, find hospitals, pharmacies, and more.}
  \resumeSubHeadingListEnd

\section{Class-Related Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Cache Simulator}
      {Simulation to evaluate how a variety of cache configurations perform on given memory traces from different benchmark programs.}
    \resumeSubItem{Classical IRC Chat System}
      {Developed a chat client program that communicates synchronously with a server in real-time.}
  \resumeSubHeadingListEnd

%-----------Other Work Experience-----------------
\section{Other Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Johns Hopkins University Office of Undergraduate Admissions}{Baltimore, MD}
      {Admissions Supervisor and Coordinator}{January 2023 - Present}
      \resumeItemListStart
        \resumeItem{Tour Guide Training and Evaluation}
          {Trained and evaluated all tour guides to increase positive tour reviews by 60\% and equipped new hires with tools for answering tough questions.}
        \resumeItem{Event Coordination and Organization}
          {Communicated and organized vendors, class visits, and residence hall tours for Prospective Student and Admitted Student Visit Days.}      
      \resumeItemListEnd

    \resumeSubheading
      {Starbucks Coffee Company}{Baltimore, MD}
      {Barista}{July 2023 - Present}
      \resumeItemListStart
        \resumeItem{Precision in a Fast-Paced Environment}
          {Worked in a fast-paced environment where accuracy and precision were as critical as customer support and connection, helping create the "Third Place" and contributing to a 20 point increase in Customer Connection Scores.}
        \resumeItem{Multi-Tasking and Collaboration}
          {Managed multiple roles and multi-tasked in a high stress environment, experienced in teamwork and collaboration.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
  

%--------PROGRAMMING SKILLS------------
\section{Other}
  \resumeSubHeadingListStart
     \resumeSubItem{Roles}
      {Eclectics Dance Team Marketing and Technical Operations Chair}
    \resumeSubItem{Languages}
      {English (First Language), Chinese, Korean, Spanish}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
